\section*{Strategy:}
\begin{itemize}
    \item Applications for grad school.
    \item Timing is the main thing here, even if you're not fully ready.
    \item Take risks sometimes. Like long shots. If it happens, it'll be really cool!
    \item Don't blindly apply to things make sure they fit into a larger picture.
    \item Have one document for your long term vision. Shaping how you want your life in 10-15 years. And another one for short-term. Like this year whats going on.
    \item Keep track of the conferences \& their deadlines. Workshops too. Plan your year according to the global calendar, so you'll collaborations, results, etc. all match it $\rightarrow$ part of timing.
    \item Keep it secret though, except for mentors.
    \item Look for scholarships / funding / grants too. For students, keep the radar on. Maybe try a few.
    \item Never stop observing $\rightarrow$ your peers, your idols, anyone. Always think what can I learn from them. It'll enhance your strategy \& give you better ideas.
    \item Make sure you're doing atleast one thing better than last time with each project.
\end{itemize}

\subsection*{Grit:}
\begin{itemize}
    \item Fix 1 ``easy'' \& 1 ``hard'' open problem. This must not change for the rest of the semester.
    \item This is separate from your project problem statements.
    \item You must spend atleast few hours a week on it. Even if its just aimlessly staring at it, you must do it.
    \item No help policy. Do on your own. Can be by any means.
\end{itemize}

\subsection*{Networking:}
\begin{itemize}
    \item Don't talk about your own plans ever, to anyone.
    \item Prepare some questions you can ask people/profs in breaks during conferences.
    \item Check people's website, especially not shot people. On there look for educational backgrounds, areas of interest (pubs) + collaborators $\rightarrow$ who do they usually publish with.
    \item Find out who are the role models (like Danupon). Follow their websites regularly. Understand their trajectory \& find ways to reach their network.
    \item Try to work with different people \& build your network over US too.
    \item Arindam Sir has in US more.
    \item Identify \textbf{hubs} \& how to get there, even if you don't go $\rightarrow$ keep tabs on what's going on!
\end{itemize}


\subsection*{SPI 9.5+:}
\begin{itemize}
    \item You already know the drill: let 1 month pass $\rightarrow$ understand the prof \& their patterns \& materials, etc. $\rightarrow$ after midsem complete most of the syllabus on your own $\rightarrow$ revise for endsem.
    \item Don't try to understand anything much here. Optimize to score.
    \item Don't play last min games with your health though. Keep a steady pace. Maybe study once a week (weekends?).
\end{itemize}

\subsection*{Non-academic discipline:}
\begin{itemize}
    \item Must daily before lunch slot.
    \item Evening go to play for 45 min. (Maybe morning practice?).
    \item Sleep at 11:00--11:30 everyday!
    \item Do meditation in morning or evening daily.
    \item 1 hour detox at night (starting 10:30pm) $\rightarrow$ read, journal, sing, talk, etc.
    \item Watch shift in day 100\%.
    \item Go out on weekends!
    \item Enjoy! Don't rush! Keep up the good thinking / emotional processing stuff!
\end{itemize}